---
title: "aaa"
author: "kuntal"
date: "2/15/2023"
output: pdf_document
---

```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
knitr::opts_chunk$set(echo = TRUE)
```



# Multiple Linear Regression

# Importing the dataset
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
dataset = read.csv('50_Startups.csv')
```
# Encoding categorical data
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
dataset$State = factor(dataset$State,
                    levels=c('New York', 'California', 'Florida'),
                    labels=c(1,2,3))
```
# Splitting the dataset into the Training set and Test set
# install.packages('caTools')
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
library(caTools)
set.seed(123)
split = sample.split(dataset$Profit, SplitRatio = 0.8 )
training_set = subset(dataset,split== TRUE )
test_set = subset(dataset,split== FALSE )
```

# Feature Scaling
# training_set = scale(training_set)
# test_set = scale(test_set)

# Fitting Multiple Linear Regression to the Training set

# can be also written as if you want selected independent columns and . for all columns
#regressor = lm(formula = Profit ~ R.D.Spend + Administration + Marketing.Spend + State, 
#               training_set)
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
regressor = lm(formula = Profit ~ . ,
               data = training_set)

summary(regressor)
```
#Analizing the result of summery coffecient we see R.D.Spend has the maximum effect as P-value is minimum and has 
# "***" statistical significance
# that gives the benefit that we can also use simple linear regression for faster process 
#like  formula = Profit ~ R.D.Spend that will be ok and will give same prediction


# Predicting the Test set results
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
y_pred = predict(regressor, newdata = test_set)
```

#building optimum modal using backward elimination

#Backward Elimination 
#Step1 - select significance level (SL) to stay in the modal (eg SL =.05)
#Step2 - fit the full modal with all possible predictor
#Step3 - consider the predictor with the highest P-Value. if P > SL go to step 4 otherwise go to FIN  (finish Modal is ready)  
#Step4 - remove the predictor 
#Step5 - fit the modal without the variable* (Note* means rebuild the modal again so if 100 after remove its 99 you have the rebuild the modal with 99 variable) go 		  back to Step 3 till (not P > SL)

#you can take training set also instead of whole dataset
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
regressor = lm(formula = Profit ~ R.D.Spend + Administration + Marketing.Spend + State, 
               data = dataset)

summary(regressor)
```
#remove independent variable one by one where P-value > than .05 or 5% in Coefficients
#first remove State has very high  P-value 99% and 93% no  statistical significance or impact on dependent variable Profit  
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
regressor = lm(formula = Profit ~ R.D.Spend + Administration + Marketing.Spend, 
               data = dataset)

summary(regressor)
```
#remove Administration has very high P-values %60 no statistical significance or impact on dependent variable Profit  
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
regressor = lm(formula = Profit ~ R.D.Spend +  Marketing.Spend, 
               data = dataset)
summary(regressor)

y_pred = predict(regressor, newdata = test_set)
y_pred
```

#You can see  R.D.Spend excellent impact on Profit 
# but now you can also see Marketing.Spend has some  statistical significance 
#remove Marketing.Spend as it is > 5% following strictly the elimination rules
#Note You may think about it to keep also

```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
regressor = lm(formula = Profit ~ R.D.Spend, 
               data = dataset)
summary(regressor)
y_pred = predict(regressor, newdata = test_set)
y_pred
```

#Note: So  final modal is either based on one independent variable R.D.Spend or
# team with R.D.Spend +Marketing.Spend depending upon your choice
# now need check adjusted R squared and  R squared and 
# then choose based on adjusted R squared  near to 1 for best modal

# Note:Coefficient are correlated to between dependent and independent variable 
# these are measured per unit. since here we are talking in dollars
# +ve mean increase and -ve means decrease
# R.D.Spend per unit(dollar) increase the profit per unit (in dollar) 
# by 7.9 cent and similarly for marketing. Always treat it as Per Unit both variable

#Also Coefficient talk about the additional effect of every single variable
# given that the other variable already in place. example here R.D.Spend already 
# in the modal and Marketing.Spend give additional effect
 
###Automated Code for Backward Elimination
```{r, echo = TRUE, message = FALSE, warning = FALSE, eval = TRUE}
backwardElimination <- function(x, sl) {
  numVars = length(x)
  for (i in c(1:numVars)){
    regressor = lm(formula = Profit ~ ., data = x)
    maxVar = max(coef(summary(regressor))[c(2:numVars), "Pr(>|t|)"])
    if (maxVar > sl){
      j = which(coef(summary(regressor))[c(2:numVars), "Pr(>|t|)"] == maxVar)
      x = x[, -j]
    }
    numVars = numVars - 1
  }
  return(summary(regressor))
}

SL = 0.05
dataset = dataset[, c(1,2,3,4,5)]
backwardElimination(training_set, SL)
```